--- 
title: "Bookdown, Travis, Fonts"
author: "Lukas Burk"
date: "Stand: `r withr::with_locale(c('LC_TIME' = 'de_DE'), format(Sys.time(), '%d. %B %Y %H:%M Uhr', tz = 'Europe/Berlin'))`"
lang: de-DE
site: bookdown::bookdown_site
url: ''
documentclass: scrartcl
bibliography: ["book.bib", "packages.bib"]
biblio-style: apalike
link-citations: yes
colorlinks: true
papersize: a4
mainfont: "Source Serif Pro" # "TeX Gyre Pagella"
sansfont: "Source Sans Pro" # "TeX Gyre Heros"
monofont: "Source Code Pro"
monofontoptions:
  - Mapping=tex-ansi
  - Scale=0.8
mathfont: "Asana Math"
always_allow_html: yes
links-as-notes: yes
github-repo: "jemus42/bookdown-debugging"
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

